    %-------------------------
% Resume in Latex
% Author
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Elia Trevisan, PhD} % Your Name
\newcommand{\currentpos}{Machine Learning for Humanoids @ Foundation} % Your Program
\newcommand{\edutitle}{MSc Systems \& Control} % Your Roll No.
\newcommand{\phone}{+49 1741521968} % Your Phone Number
\newcommand{\emaila}{elia.trv@gmail.com} %Email 1

\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------

{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ \phone}\\
  {\currentpos} & \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}} \\
  {Munich, Germany} & \href{https://eliatrevisan.com}{\raisebox{0.0\height}{\footnotesize \faGlobe}\ {eliatrevisan.com}} \\  
\end{tabularx}
}

Reinforcement leaning, motion planning and control engineer with expertise in gradient-free optimization methods (MPPI, CEM) and RL locomanipulation. Background in system identification, control theory, autonomous driving, and manipulation. I love solving hard problems, from theory to hardware.


%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Machine Learning Engineer - Humanoid Locomanipulation}{}
      {Foundation, Munich, Germany}{April 2026 - Present}
        \vspace{-1.5mm}
      \resumeItemListStart
    \item {I lead the development of RL-based whole body controllers for humanoids as part of the AI team.}
    \resumeItemListEnd
    \resumeSubheading
      {Software Engineer - Robot Control}{}
      {Neura Robotics, Stuttgart, Germany}{November 2025 - March 2026}
        \vspace{-1.5mm}
      \resumeItemListStart
    \item {Developed motion planning and control software for humanoids, collaborative industrial arms, mobile manipulators, and autonomous mobile robots.}
    \resumeItemListEnd

    \resumeSubheading
      {PhD and Postdoc - Robot Motion Planning}{}
      {TU Delft, Netherlands}{October 2020 - June 2025}
        \vspace{-1.5mm}
        \resumeItemListStart
            \item {Contributed to optimization and sampling-based Model Predictive Control (MPC) (e.g., MPPI), Risk-Awareness, Machine Learning (ML) for trajectory prediction, and collaborated on Task and Motion Planning (TAMP).}\vspace{0.5mm}
            \item {Applied planners to \textbf{vessels} (Roboat) in outdoor environments, \textbf{ground robots} (Jackal), and \textbf{mobile manipulators} (Boxer with Panda arm) for pushing and grasping using \textbf{Isaac Gym} as a dynamic model.}\vspace{0.5mm}
            \item {\textbf{Mentored ten students}, of which six master thesis, one internship, one master research assignment, and two bachelor projects. All students were very successful, and \textbf{all} theses were \textbf{included in a publication}.}\vspace{0.5mm}
            \item {Published several papers in \textbf{top robotics workshops, conferences and journals} (ICRA, IROS, MRS, RAL), with \textbf{two} nominated \textbf{Best Paper Finalists}.}
            \item {PhD \textbf{thesis} was a \textbf{finalist} for the \textbf{IEEE RAS TC-MRS Best Dissertation Award}.}
        \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant - Systems \& Control}{}
      {TU Delft, Netherlands}{Sep 2019 - Jun 2020}
        \vspace{-1.5mm}
      \resumeItemListStart
    \item {Mentored master students in core control courses (Introduction Project, Nonlinear Systems Theory, Integration Projects), trusted by faculty to guide students through complex assignments and projects.}
    \resumeItemListEnd

    \resumeSubheading
      {Board Member - Systems \& Control Student Association}{}
      {DSA Kalman, TU Delft}{Mar 2019 - Mar 2020}
        \vspace{-1.5mm}
      \resumeItemListStart
    \item {Organized course evaluations, maintained association website, and coordinated social and industry events.}
        \resumeItemListEnd

    \resumeSubheading
      {PLC Programmer - Industrial Automation}{}
      {Tecnoquadri, Italy}{Mar 2018 - Aug 2018}
        \vspace{-1.5mm}
      \resumeItemListStart
    \item {Designed PLC software for production lines and coordinated installation across factories. Hands-on experience with industrial robots and automation, wiring electrical panels, and mechanical systems.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-5.5mm}


%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
        {MSc in Systems and Control}{\textit{\textbf{Cum Laude}}}
        {TU Delft, Netherlands}{Sep 2018 - Aug 2020}
        \vspace{-1.5mm}
        \resumeItemListStart
            \item {Courses on control theory, robust and multivariable control design, filtering \& identification, optimization in systems and control, nonlinear systems theory, model predictive control, adaptive control, fault diagnosis and fault tolerant control, digital control.}
            \item {Graduated \textbf{top of my class}, thesis with Prof. Michel Verhaegen on modeling and identification for High Numerical-Aperture microscopy. Developed an algorithm that could both retrieve a clear image of the specimen and estimate the aberration in the microscope from very few out-of-focus images via alternating projections.}
        \resumeItemListEnd
    \resumeSubheading
        {BSc in Automation Engineering}{}
        {University of Bologna, Italy and Tongji University, China}{Sep 2014 - Feb 2018}
        \vspace{-1.5mm}
        \resumeItemListStart
            \item {\textbf{Won} AlmaTong, \textbf{a merit-based scholarship} to perform half of the bachelor's at Tongji University in Shanghai.}
            \item {Courses on automatic controls, mechanics, electronics, computer architectures, automatic machines, and robotics.}
            \item {Led a collaboration between my university and Electrolux and developed a simulator in Gazebo, using ROS, MoveIt, and Aruco markers to detect and manipulate household appliances with a UR5 Robot.}
        \resumeItemListEnd
    \resumeSubheading
        {Electrical Engineering High School}{}
        {ITST J.F. Kennedy, Italy}{Sep 2009 - Jul 2014}
        \vspace{-1.5mm}
        \resumeItemListStart
            \item {Theory and laboratories on electric machines, control, and design of civilian and industrial power systems.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-5.5mm}





\newpage

%-----------Technical skills-----------------
\section{\textbf{Skills and Interests}}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textbf{Programming}{: Proficient in C/C++, Python (with PyTorch), Matlab, Simulink, Siemens TIA Portal, beginner in CUDA, HTML and CSS.} \\
     \vspace{1.0mm}
     \textbf{Robotics}{: Competent in ROS1 and ROS2, motion capture (Vicon and OptiTrack), experience with Lidar Odometry (KISS-ICP and LIO-SAM), Gazebo, Pybullet, IsaacGym, Mujoco, and several robotics platforms.}\\
     \vspace{1.0mm}
     \textbf{Development}{: Git, Docker, CI/CD pipelines, cloud storage (AWS S3), Linux.} \\
     \vspace{1.0mm}
     \textbf{Languages}{: Fluent in Italian and English, beginner in Spanish and Polish.}\\
     \vspace{1.0mm}
     \textbf{Personal Interests}{I build stuff also outside working hours, but it's usually made out of wood. I competed in athletics many years ago. I now still enjoy running, but I recently got into bouldering. I love to hike, and I miss my Alps! I always snorkel when I get the chance. I've recently scuba-dived on the reef in Okinawa and have wanted to get a license since then. I used to play the drums as a teenager, and I am still always up for some good live music.} \\
    }}
 \end{itemize}
 \vspace{-16pt}



% %-----------Positions of Responsibility-----------------
% \section{\textbf{Positions of Responsibility}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{On Desk Registrations Volunteer } % Position
%     {Aarhant Cyber Week Event - RCOEM, Nagpur} %Club,Event
%     {Oct - Dec 2022} %Tenure Period \\
%     \resumeItemListStart
%     \item {Helped to attract close to 300 attendees to the event.}
%     \item {Collected over Rs. 20,000 in entry fees for different activities.}
%     \resumeItemListEnd

% \resumeSubHeadingListEnd
% \vspace{-5mm}




% %-----------Achievements-----------------
% \section{\textbf{Achievements}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
    
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
% \resumeSubHeadingListEnd
% \vspace{-5mm}



%-------------------------------------------
\end{document}
